---
title: "Individual Assignment 2"
author: "Megha Deshmukh 24230928"
format: 
  html: 
    embed-resources: true
    toc: true
    theme: flatly
    toc-depth: 2
    toc-title: "Contents"
    code-fold: true
---
## Introduction 
This assignment focuses on analyzing data related to cyberattacks and their effects on industries. The goal is to explore three datasets: Cyberattack Data, Compliance Data, and Data Breach Data.
The aim is to combine these datasets to understand how industries are affected by cyberattacks and security controls effectiveness against breaches together with their resulting data losses. My research will offer guidance to businesses as well as policymakers for enhancing cybersecurity through integrated findings.

#### Dataset 1: [Cyberattack Data](https://www.kaggle.com/datasets/shakirul09/cyber-crimes-dataset).
The dataset provides information about different types of cyberattacks together with the targeted systems' results after attacks. The database provides information about distinct cyberattack forms and industry targets with data loss measurement data.

#### Dataset 2: [Data Breach and Control Data](https://catalog.data.gov/dataset/data-breach-notifications-affecting-washington-residents-personal-information-breakdown)
The dataset examines security controls together with compliance measures that organizations implement for securing their operations. This database shows how well security controls operate through compliance scoring which aids organizations in defending themselves from cyber threats.

#### Dataset 3: [Compliance Information](https://catalog.data.gov/dataset/5-12-cybersecurity-detail-d8bb7)
The dataset contains comprehensive information about recent data breaches which shows their origins together with the business sectors they targeted and the number of people affected. The data show different breach types, breach lengths and which industries experience the greatest risk of lost data.


## Flow Digram using mermaid for cyber crime dataset

```{mermaid}
  graph TD
    A[Start] --> B[Load Dataset1 & Dataset3]
    B --> C[Group Dataset3 by Industry & Attack Type]
    C --> D[Summarize Total Affected Users]
    D --> E[Filter Attack Types (Phishing, Malware, etc.)]
    E --> F[Create Pie Chart: Total Affected Users by Industry]
    B --> G[Combine Dataset1 & Dataset3]
    G --> H[Summarize Attack Types & Severity]
    H --> I[Create Bar Chart: Total Data Compromised by Attack Type & Industry]
    I --> J[Generate Insights]
    F --> J
    J --> K[End]
```

## Loaded necessary libraries

```{r setup ,message=FALSE,warning=FALSE}

library(tidyverse)
library(dplyr)
library(plotly)
library(formattable)
library(RColorBrewer)
library(data.table)

library(ggplot2)




```


# Load necessary libraries


```{r datu ,message=FALSE,warning=FALSE}
# Read only necessary columns
file_path1 <- "/Users/meghadeshmukh/Desktop/R_Assignment/cybersecurity_large_synthesized_data.csv"
file_path2 <-"/Users/meghadeshmukh/Desktop/R_Assignment/Global_Cybersecurity_Threats_2015-2024.csv"
file_path3 <-"/Users/meghadeshmukh/Desktop/R_Assignment/Data_Breach_Notifications_Affecting_Washington_Residents__Personal_Information_Breakdown_.csv"
  
dataset1 <- fread(file_path1, select = c("attack_type", "industry", "attack_severity", "security_tools_used","data_compromised_GB","location","outcome"))

dataset2 <- fread(file_path2, select = c("Attack Type","Defense Mechanism Used","Target Industry","Number of Affected Users", "Country" ))
dataset2 <- dataset2 %>%
  rename(
    attack_type = "Attack Type",
    defence_mechanism_used = "Defense Mechanism Used",
    target_industry = "Target Industry"
  )

dataset3 <- fread(file_path3, select = c("CyberattackType","IndustryType","WashingtoniansAffected", "Year", "WashingtoniansAffectedRange", "BreachLifecycleRange", "EntityState","DateSubmitted","DateStart","DateEnd"))
dataset3 <- dataset3 %>%
  rename(
    attack_type = "CyberattackType",
    no_affected_user="WashingtoniansAffected"
  )

filtered_dataset1 <- dataset1 %>%
  filter(outcome == "Success"  & data_compromised_GB > 5) %>%
  select(attack_type, industry, attack_severity,security_tools_used,data_compromised_GB,location)


#merged_data <- merge(dataset1_clean, dataset2_clean, by = "attack_type")
dataset1_dataset2 <- filtered_dataset1 %>%
  inner_join(dataset2, by = "attack_type")
head(dataset1_dataset2)



country_attack <- dataset1_dataset2 %>%
  group_by(target_industry, attack_type) %>%
  summarise(count = n())


# A bubble graph was plotted using Plotly.
plot_ly(country_attack, 
        x = ~target_industry, 
        y = ~attack_type, 
        size = ~count, 
        color = ~attack_type, 
        type = 'scatter', 
        mode = 'markers', 
        hoverinfo = 'text',  
        text = ~paste('Count of attack type based on industry: ', count),
        marker = list(sizemode = 'diameter', opacity = 0.5)) %>%
  layout(title = "Attack Types by Country",
         xaxis = list(title = "Most Targeted Industries"),
         yaxis = list(title = "Major Types of Attack happened"))

attack_counts <- dataset1_dataset2 %>%
  count(attack_type)



```


#dataset3 operations
```{r rjsetup33 ,message=FALSE,warning=FALSE}
# Grouping data by IndustryType and CyberattackType
data_grouped <- dataset3 %>%
  group_by(IndustryType, attack_type) %>%
  summarise(total_affected = sum(no_affected_user), .groups = "drop")%>%
  filter(!is.na(total_affected)) %>%
  filter(attack_type %in% c("Phishing", "Malware", "Ransomware","Other"))

plot_ly(data_grouped, 
        labels = ~attack_type, 
        values = ~total_affected, 
        type = "pie", 
        textinfo = "label+percent", 
        hoverinfo = "label+value+percent",
        marker = list(colorscale = 'Rainbow')) %>%
  layout(title = "Total Affected Users by Industry")
```


# New trial

```{r rnsetup33 ,message=FALSE,warning=FALSE}
# Group by attack_type and industry, and sum the data compromised

total_data_compromised <- dataset1_dataset2 %>%
  group_by(attack_type, defence_mechanism_used) %>%
  summarise(total_data = sum(attack_severity))

head(total_data_compromised)

plot_ly(total_data_compromised, 
        x = ~attack_type,           
        y = ~total_data,            
        color = ~defence_mechanism_used,          
        type = 'bar', 
        text = ~paste('defence mechanism used: ', defence_mechanism_used, '<br>attack severity: ', total_data, 'GB'),
        hoverinfo = 'text') %>%
  layout(title = "Total Data Compromised by Attack Type and Industry",
         xaxis = list(title = "Attack Type"),
         yaxis = list(title = "Total Data Compromised (GB)"))

```






